---
title: "Lecture 1"
output: html_notebook
---

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

```{r}
plot(cars)
```

```{r}
ysamp = sample(1:6,600,replace=T)
hist(ysamp)
```

runif generates outcomes of uniform random variable  
__QUESTION__: What is the plot argument?
```{r}
hist(1 + 3*runif(1000), prob=T)
```
Bernoulli
```{r}
n = 1000
p = 0.3
ysamp = as.integer(runif(n) > p)
hist(ysamp, prob=T)
```
Binomial
```{r}
n = 100
p = 0.5
# represents just one run of the binomial
ysamp = sum(as.integer(runif(n) < p)) 
```
Discrete distribution  
__QUESTION__: How to generate the discrete distribution nicely?
```{r}
p <- c(0.1,0.2,0.3,0.1,0.1,0.2)
x <- c(1  ,2  ,3  ,4  ,5  ,6)
sum(p)
```
cdf = x^3
```{r}
n <- 10000
u <- runif(n)
x <- u^(1/3)
hist(x, prob=TRUE)
y <- seq(0, 1, .01)
lines(y, 3*y^2)
```
Exponential distribution cdf = 1 - exp(-lambda * x)
```{r}
n <- 1000
lambda <- 1.5
hist(-log(runif(n))/lambda)
hist(rexp(n, lambda))
```
Code for Beta sampler
```{r}
n <- 1000
k <- 0
j <- 0
y <- numeric(n)
c <- 3/2

while (k < n) {
  u <- runif(1)
  j <- j + 1
  x <- runif(1)
  if (6 * x * (1-x) > c * u) {
    k <- k+1
    y[k] <- x
  }
}

j / n # compare with c

```
Quantile comparison
```{r}
qs <- seq(0.01,0.99,by=0.01)
steratio <- sqrt(qs*(1-qs))/dnorm(qnorm(qs))
plot(qs, steratio, 
     type="l", # type of the plot - lines
     xlab="Quantile", ylab="Ratio ste(quantile)/ste(mean))",
     lwd=3, # line width
     col=4, # color
     ylim=c(1, 4)
     )
#plot(qs,steratio,col=4,las=1,lwd=3,type="l",xlab="quantile",
#     ylab="Ratio ste(quantile)/ste(mean)",ylim=c(0.5,1))
```

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.